---
title: "Bodyweight Data Analysis (3 Diets)"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(stats)
library(dunn.test) # For post-hoc analysis
```

Load Data
Code snippet
```{r}
bodyweight_data <- read.csv("bodyweight_data_3_diets.csv")
```

Distribution Histograms
Code snippet

```{r}
ggplot(bodyweight_data, aes(x = Bodyweight, fill = Diet)) +
  geom_histogram(alpha = 0.5, position = "identity") +
  facet_wrap(~ Diet) +
  labs(title = "Distribution of Bodyweight by Diet",
       x = "Bodyweight",
       y = "Frequency") +
  theme_minimal()
```


The histograms show the distribution of bodyweight for each diet. The right skewness is evident.

Boxplots
Code snippet

```{r}
ggplot(bodyweight_data, aes(x = Diet, y = Bodyweight)) +
  geom_boxplot() +
  labs(title = "Boxplot of Bodyweight by Diet",
       x = "Diet",
       y = "Bodyweight") +
  theme_minimal()
```


The boxplots visually compare the bodyweight distributions between the three diets.

Shapiro-Wilk Normality Test
Code snippet

```{r}
shapiro_diet1 <- shapiro.test(bodyweight_data$Bodyweight[bodyweight_data$Diet == "Diet 1"])
shapiro_diet2 <- shapiro.test(bodyweight_data$Bodyweight[bodyweight_data$Diet == "Diet 2"])
shapiro_diet3 <- shapiro.test(bodyweight_data$Bodyweight[bodyweight_data$Diet == "Diet 3"])

cat("Shapiro-Wilk test for Diet 1:\n")
print(shapiro_diet1)
cat("\nShapiro-Wilk test for Diet 2:\n")
print(shapiro_diet2)
cat("\nShapiro-Wilk test for Diet 3:\n")
print(shapiro_diet3)
```


The Shapiro-Wilk test assesses the normality of the bodyweight data within each diet. The low p-values indicate that the data significantly deviates from a normal distribution.

Kruskal-Wallis Test
Code snippet

```{r}
kruskal_result <- kruskal.test(Bodyweight ~ Diet, data = bodyweight_data)
print(kruskal_result)
```

The Kruskal-Wallis test is used to compare the bodyweight distributions between the three diets, as the data is not normally distributed. The low p-value indicates a significant difference between at least two diets.

Post-Hoc Analysis (Dunn Test)
Code snippet
```{r}
dunn_result <- dunn.test(bodyweight_data$Bodyweight, bodyweight_data$Diet, method = "bonferroni")
print(dunn_result)
```

The Dunn test is used for post-hoc pairwise comparisons to determine which specific diets differ significantly from each other. The Bonferroni correction is applied to adjust for multiple comparisons.