---
title: "Bodyweight Data Analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(stats)
```


Load Data
Code snippet

```{r}
bodyweight_data <- read.csv("bodyweight_data.csv")
bodyweight_data
```

Distribution Histograms
Code snippet

```{r}
ggplot(bodyweight_data, aes(x = Bodyweight, fill = Diet)) +
  geom_histogram(alpha = 0.5, position = "identity") +
  facet_wrap(~ Diet) +
  labs(title = "Distribution of Bodyweight by Diet",
       x = "Bodyweight",
       y = "Frequency") +
  theme_minimal()
```

The histograms show the distribution of bodyweight for each diet. The right skewness is evident, as expected from the data generation.

Boxplots
Code snippet
```{r}
ggplot(bodyweight_data, aes(x = Diet, y = Bodyweight)) +
  geom_boxplot() +
  labs(title = "Boxplot of Bodyweight by Diet",
       x = "Diet",
       y = "Bodyweight") +
  theme_minimal()
```
The boxplots visually compare the bodyweight distributions between the two diets. The difference in medians is apparent, and the skewness is also observable.

Shapiro-Wilk Normality Test
Code snippet
```{r}
shapiro_diet1 <- shapiro.test(bodyweight_data$Bodyweight[bodyweight_data$Diet == "Diet 1"])
shapiro_diet2 <- shapiro.test(bodyweight_data$Bodyweight[bodyweight_data$Diet == "Diet 2"])

cat("Shapiro-Wilk test for Diet 1:\n")
print(shapiro_diet1)
cat("\nShapiro-Wilk test for Diet 2:\n")
print(shapiro_diet2)
```
The Shapiro-Wilk test assesses the normality of the bodyweight data within each diet. The low p-values indicate that the data significantly deviates from a normal distribution, confirming the visual assessment of skewness.

Mann-Whitney U Test
Code snippet

```{r}
mann_whitney_result <- wilcox.test(Bodyweight ~ Diet, data = bodyweight_data)
print(mann_whitney_result)
```